{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-04-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

        We introduce two examples variants of line search method used to enhence the accelerated proximal gradient methods in the literatures to demonsrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  

@@

@@

    \section{Practical enhencements}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section.

>>>>

        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  

@@

            This example won't give specific rules for calculating $\tilde x_k$ for monotone descent. 
            Chambolle's restart has specific rules for choosing the step sizes based on the estimates of the Lipschitz constants. 

@@

    \section{Practical enhancement}
        In this section, we provide results for the faster convergence rate of examples listed from the previous section. 
    \section{Restarting with gradient and function values}

\section{Primal Dual Lagrangian for LP}
